Learning Reusable Components for Neurally--Guided Bayesian Program Learning

### 2018-05-12 nips_2018.tex
more writing

\subsection{Symbolic Regression}\label{regressionSection}
We show how to use \system to infer programs containing both discrete
structure and continuous parameters. The high-level idea is to write programs with unspecified real-valued parameters, and to fit those parameters by differentiating through the program
and optimizing using gradient descent.
We task our model
with solving 200 symbolic regression problems, each a polynomial of
degree 1 to 4, where our observations $x$ are 10
input/output examples.%, which we write as $x = \left\{(i_n,o_n)
%\right\}_{n\leq N}$. %% For example, one task is to infer a program
%% calculating $3x + 2$, and the observations are the input-output
%% examples $\left\{(-1,-1),(0,2),(1,5) \right\}$.

We initially give our system only addition and multiplication,
along with the possibility of introducing real-valued parameters, which we write as $\mathcal{R}$.
We define the likelihood of an observation $x$ by assuming a Gaussian noise model for the input/output examples,
and penalize the use of continuous parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.
%% \begin{align*}
%%   \log \probability[x|p] \triangleq& \sum_{n\leq N}\log
%%   \mathcal{N}(p(i_n,\vec{\mathcal{R}}^*)|o_n) - \frac{D\log N}{2}
%% \end{align*}

@@

\begin{table}[t]
  \centering
  \begin{tabular}{c}
    String editing primitives\\
    \begin{tabular}{l}
    \toprule
    \code{0}, \code{+1},\code{-1},\codechar{},\codechar{,},\codechar{ },\codechar{<},\codechar{>}  \\
    \code{split}, \code{join}, \code{map}, 
    \code{+}, \code{chr->str}, \code{trim}, \code{nth}\\
    \code{length}, \code{slice},    \code{lower}, \code{upper}, \code{capitalize}
  \\\bottomrule
    \end{tabular}\\
\\    Subset of learned DSL\\
    \begin{tabular}{l}
      \toprule
      $f_0($\code{c}$) \,=\, $\code{(+ (chr->str c))}\\
      $f_1($\code{i$,$c$,$s}$) \,=\, $\code{(+ (nth i (split c s))}\\
        \phantom{$f_1($\code{i$,$c$,$s}$) \,=\, $\code{(+ }}\code{(chr->str c))}\\
      $f_2($\code{s$,$c}$) \,=\, $\code{((}$f_0$\code{ c) (}$f_1$\code{ (+1 0) c s))} \\
        \hspace{0.5cm}($f_2$: \emph{Extract substring delimited by character})\\
      $f_3($\code{c$,$s}$) \,=\, $\code{(nth (+1 0) (split c (nth 0 s)))}\\
        \hspace{0.5cm}($f_3$: \emph{2nd substring delimited by character})
    %% $f_0($\code{i,c,s}$) = $    \code{(+ (index i (split c s)) (chr->str c))}\\
    %% $f_1 = $\code{(join "")}
  \\\bottomrule
    \end{tabular}
  \end{tabular}
  \caption{Top: provided string editing primitives. Bottom: some learned DSL primitives.}\label{textPrimitives}
  \end{table}

>>>>

\subsection{Symbolic Regression}\label{regressionSection}
We show how to use \system to infer programs containing both discrete
structure and continuous parameters. The high-level idea is to write programs with unspecified real-valued parameters, and to fit those parameters by differentiating through the program
and optimizing using gradient descent.
We task our model
with solving 200 symbolic regression problems, each either a polynomial of
degree 1 to 4 or a rational function.
The recognition model is a convolutional network that observes an image
of the target function's graph (Fig.~\ref{functions}) --
visually, different kinds of polynomials and rational functions
produce different kinds of graphs,
and so the recognition model must learn to
look at a graph and predict what kind of function best explains it.
\begin{wrapfigure}{r}{0.3\textwidth} \newcommand{\functionSize}{0.75cm}
  \includegraphics[width = \functionSize]{figures/functions/0.png}
  \includegraphics[width = \functionSize]{figures/functions/6.png}
  \includegraphics[width = \functionSize]{figures/functions/207.png}
  \includegraphics[width = \functionSize]{figures/functions/160.png}
  \includegraphics[width = \functionSize]{figures/functions/303.png}\\  
  \includegraphics[width = \functionSize]{figures/functions/402.png}
  \includegraphics[width = \functionSize]{figures/functions/415.png}
  \includegraphics[width = \functionSize]{figures/functions/426.png}
  \includegraphics[width = \functionSize]{figures/functions/597.png}
  \includegraphics[width = \functionSize]{figures/functions/591.png}
  \caption{Recognition model input for symbolic regression. While the DSL learns subroutines for rational functions \& polynomials, the recognition  model jointly learns to look at a graph of the function (above) and predict which of those subroutines is appropriate for explaining the observation.}\label{functions}
  \end{wrapfigure}

We initially give our system addition, multiplication, and division,
along with the possibility of introducing real-valued parameters, which we write as $\mathcal{R}$.
We define the likelihood of an observation $x$ by assuming a Gaussian noise model for the input/output examples,
and penalize the use of continuous parameters using the BIC~\cite{Bishop:2006:PRM:1162264}.
%% \begin{align*}
%%   \log \probability[x|p] \triangleq& \sum_{n\leq N}\log
%%   \mathcal{N}(p(i_n,\vec{\mathcal{R}}^*)|o_n) - \frac{D\log N}{2}
%% \end{align*}

@@

\begin{table}[t]
  \centering
    \begin{tabular}{l}
      \toprule
      $f_0($\code{a}$,$\code{b}$) \,=\, $\code{(fold a b (lambda (x y) (cons x y))))))}\\
      \hspace{0.5cm}($f_0$: \emph{Appends lists (of characters))}\\
      $f_1($\code{s}$,$\code{c}$) \,=\, $\code{(fold s s (lambda (a x) (cdr (if (= c x) s a))))}\\
        \hspace{0.5cm}($f_1$: \emph{Drop first characters from }\code{s}\emph{ until  }\code{c}\emph{ reached})\\
      $f_2($\code{s}$) \,=\, $\code{(unfold s empty? car (lambda (z) (}$f_1$\code{ z SPACE)))}\\
        \hspace{0.5cm}($f_2$: \emph{Abbreviates a sequence of words})
  \\\bottomrule
    \end{tabular}
  \caption{Some learned DSL primitives for string editing}\label{textPrimitives}
  \end{table}
